### 2021-05-27 geography/ia/paper.tex
added graphs for questionnaire -> toward final draft

\subsubsection{Questionnaire}

@@

Once our data collected, we can analyse certain patterns or appearances that do not follow a general trend. Our data is shown below in Subsection \ref{sec:data}.

@@

The dataset collected from the questionnaire is shown in the tables in Figures 10, 11.

@@

@@

There are some processes in our paper that would be done differently if done now. For example:

>>>>

\subsubsection{Questionnaire}
\label{sec:questionnaire}

@@

Once our data collected, we can analyse certain patterns or appearances that do not follow a general trend. Our data is shown below in Section \ref{sec:data}.

@@

The dataset collected from the questionnaire (mentioned in Section \ref{sec:questionnaire}) is shown in the tables in Figures 10, 11.

@@

This data can be shown in the form of a bar graph (Figure 12), in order to visualize the distribution and for further analysis.

\begin{figure}[H]
    \centering
    \includegraphics[width=1\linewidth]{media/graphs.png}
    \caption{Graphs representing aforementioned data in Figures 10, 11}
\end{figure}

@@

There are some processes in our paper that would be done differently if done now. To list the ones I managed to find at the time of writing:
